---
title: "Analysis of Replase-Free Survival (RFS) Time for (E1684, E1690) Data Sets"
output: 
  html_notebook:
    toc: yes
    toc_float:
      collapsed: true
      smooth_scroll: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(survival)
library(hdbayes)
library(posterior)
library(ggplot2)
library(latex2exp)
library(kableExtra)
library(tables)
```


# Summary of Baseline Covariate

```{r}
## load data
hist <- E1684
curr <- E1690

## replace 0 failure times with 0.50 days
hist <- hist %>% mutate(failtime = if_else(failtime == 0, 0.50/365.25, failtime)) # 1 subject w/ failtime = 0
curr <- curr %>% mutate(failtime = if_else(failtime == 0, 0.50/365.25, failtime)) # 10 subjects w/ failtime = 0

## Center and scale age based on current data
age_stats <- with(curr, c('mean' = mean(age), 'sd' = sd(age)))
hist$cage <- ( hist$age - age_stats['mean'] ) / age_stats['sd']
curr$cage <- ( curr$age - age_stats['mean'] ) / age_stats['sd']
```

```{r}
library(gtsummary)

## create summary table
df       <- rbind(curr, hist) %>%
  mutate(
    Treatment = case_when(
      treatment == 1 ~ "Treatment",
      TRUE ~ "Control"
    ),
    Sex = factor(sex, levels = c(0, 1), labels = c("Male", "Female")),
    `Having > 1 cancerous lymph node` = case_when(
      `node_bin` == 1 ~ "Yes (> 1 node)",
      TRUE ~ "No (0 or 1 node)"
    ),
    Age = age,
    `Standardized Age` = cage
  )
df$Study <- rep(c("E1690", "E1684"), times = c(nrow(curr), nrow(hist)))

tab <- df %>%
  select(all_of(c("Treatment", "Sex", "Age", "Standardized Age", "Having > 1 cancerous lymph node", "Study"))) %>%
  tbl_summary(
    by = Study,
    statistic = list(
      all_continuous() ~ "{mean} ({sd})",
      all_categorical() ~ "{n} ({p}%)"
    ),
    digits = all_continuous() ~ 2
  ) %>%
  modify_header(label ~ "**Variable**",
                `stat_1` ~ "E1684, N = 262",
                `stat_2` ~ "E1690, N = 426")
tab
# show_header_names(tab)
```



# Frequentist Analysis

```{r}
## KM plots
library(survminer)
library(ggpubr)

curr2 <- df[df$Study == "E1690", ]
hist2 <- df[df$Study == "E1684", ]

km_fit1 <- survfit(Surv(failtime, failcens) ~ Treatment, data = curr2)
km_fit2 <- survfit(Surv(failtime, failcens) ~ Treatment, data = hist2)

xlim_range <- c(0, 10)
p1   <- survminer::ggsurvplot(km_fit1, 
                      data = curr2, 
                      pval = TRUE,
                      conf.int = TRUE,
                      palette = c("#999999", "#CC79A7"),
                      legend.labs = c("control", "treatment"),
                      ggtheme = theme_bw(),
                      xlim = xlim_range)$plot + 
  labs(subtitle = "E1690", color = "", fill = "", x = "time", y = "RFS probability") +
  theme(legend.position = "bottom",
        legend.text=element_text(size=10),
        legend.key.width= unit(2, 'cm'), 
        plot.subtitle = element_text(hjust = 0.5, size = 12)) +
  scale_x_continuous(limits = xlim_range, breaks = pretty(xlim_range))

p2   <- survminer::ggsurvplot(km_fit2, 
                      data = hist2,
                      pval = TRUE,
                      conf.int = TRUE,
                      palette = c("#999999", "#CC79A7"),
                      legend.labs = c("control", "treatment"),
                      ggtheme = theme_bw(),
                      xlim = xlim_range)$plot + 
  labs(subtitle = "E1684", color = "", fill = "", x = "time", y = "RFS probability") +
  theme(legend.position = "bottom",
        legend.text=element_text(size=10),
        legend.key.width= unit(2, 'cm'), 
        plot.subtitle = element_text(hjust = 0.5, size = 12)) +
  scale_x_continuous(limits = xlim_range, breaks = pretty(xlim_range))

KM_plts <- ggarrange(p2, p1, ncol=2, nrow=1, common.legend = TRUE, legend="bottom")
annotate_figure(KM_plts, top = text_grob("Kaplan-Meier Curves for E1684 and E1690 Data Sets", face = "bold", size = 14))
```


```{r}
## formula for current and historical data (Cox PH model)
fmla     <- Surv(failtime, failcens) ~ treatment + sex + cage + node_bin

## fit proportional hazards models on E1690 and E1684 data
fit      <- coxph(formula = fmla, data = curr)
fit.hist <- coxph(formula = fmla, data = hist)

summary(fit)
summary(fit.hist)
```


```{r}
## combine Cox PH model estimates with summary of baseline covariates 
tab.E1690.coxph <- coxph(
  Surv(failtime, failcens) ~ Treatment + Sex + `Standardized Age` + `Having > 1 cancerous lymph node`,
  data = df[df$Study == "E1690", ]
) %>%
  tbl_regression(
    label = list(
      `Sex` ~ "Sex",
      `Standardized Age` ~ "Standardized Age",
      `Having > 1 cancerous lymph node` ~ "Having > 1 cancerous lymph node"
    ),
    exponentiate = TRUE
  ) %>%
  modify_header(label ~ "**Variable**")  %>%
  modify_column_hide(columns = p.value)

tab.E1684.coxph <- coxph(
  Surv(failtime, failcens) ~ Treatment + Sex + `Standardized Age` + `Having > 1 cancerous lymph node`,
  data = df[df$Study == "E1684", ]
) %>%
  tbl_regression(
    label = list(
      `Sex` ~ "Sex",
      `Standardized Age` ~ "Standardized Age",
      `Having > 1 cancerous lymph node` ~ "Having > 1 cancerous lymph node"
    ),
    exponentiate = TRUE
  ) %>%
  modify_header(label ~ "**Variable**") %>%
  modify_column_hide(columns = p.value)

library(gt)
tab.combined <- tbl_merge(
  tbls = list(tab, tab.E1684.coxph, tab.E1690.coxph),
  tab_spanner = c("**Summary Statistics**", "**Cox PH Model for E1684**", "**Cox PH Model for E1690**")
) %>%
  as_gt() %>%
  #gt::tab_source_note("Cox PH Model: Cox proportional hazards (PH) regression model including Treatment, Sex, Standardized Age, and Having > 1 cancerous lymph node.")
  gt::tab_footnote(
    footnote = "Cox proportional hazards (PH) regression model including Treatment, Sex, Standardized Age, and Having > 1 cancerous lymph node.",
    locations = cells_column_spanners(c("**Cox PH Model for E1684**", "**Cox PH Model for E1690**"))
  )

tab.combined
```


# Bayesian Analysis 

We considered both a piecewise exponential (PWE) model (i.e., a proportional hazards model with a piece-wise constant baseline hazards) and a mixture cure rate model (referred to as the CurePWE model). The CurePWE model assumes that a fraction $p_c$ of the population is "cured", while the remaining $(1 - p_c)$ are susceptible to the event of interest. The survival function for the entire population is given by:
$$S_{\text{pop}}(t) = p_c + (1 - p_c) S(t),$$
where $S(t)$ represents the survival function of the non-cured individuals. We model $S(t)$ using a PWE model. All the covariates are incorporated through the PWE model.

For both the PWE and CurePWE models, we stratified the data sets by treatment arm and considered the number of intervals ($J$) for the piecewise constant baseline hazards varying from 2 to 9. The cut points of these intervals were selected such that each interval consists of about the same number of events in the stratified current data.

For each model, we considered the following list of priors for analysis: the reference prior, Bayesian hierarchical model (BHM), commensurate prior (CP), power prior (PP) with the discounting parameter $a_0 = 0.5$, normalized power prior (NPP), latent exchangeability prior (LEAP), and propensity score-integrated power prior (PSIPP). 

The goal is to conduct posterior inference on the difference in 2-year RFS probabilities between the IFN and control groups.

```{r}
## load compiled analysis results
results.dir <- "~/Documents/UNC/Dissertation/super prior/Code/Analysis/Results"
res         <- readRDS(file = file.path(results.dir, "compiled_analysis_results.rds"))
```


## Create Weight Plots for Each Treatment Arm

### Transform Weight Table

For display, we sum weights from $J = 2$ to $J = 9$ for the PWE/CurePWE model under each prior for each treatment arm.

```{r}
# for IFN arm
wts.tab.trt <- res$wts.tab.trt
wts.tab.trt.trans <- wts.tab.trt %>%
  mutate(is_CurePWE = grepl("CurePWE \\(J = \\d+\\)", model)) %>%
  group_by(prior, CurePWE_group = if_else(is_CurePWE, "CurePWE", "PWE")) %>%
  summarize(
    BMA = sum(BMA, na.rm = TRUE),
    `Pseudo-BMA` = sum(`Pseudo-BMA`, na.rm = TRUE),
    `Pseudo-BMA+` = sum(`Pseudo-BMA+`, na.rm = TRUE),
    Stacking = sum(Stacking, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  rename(model = CurePWE_group)
wts.tab.trt.trans <- wts.tab.trt.trans[, c("model", "prior", colnames(wts.tab.trt.trans)[-(1:2)])]

wts.tab.trt.trans <- wts.tab.trt.trans %>%
  mutate(
    prior = factor(prior, levels = c("ref", "bhm", "cp", "leap", "npp", "pp", "psipp")), 
    model = factor(model, levels = c("CurePWE", "PWE"))
  ) %>%
  arrange(model, prior)

wts.tab.trt.trans %>% mutate(across(where(is.numeric), \(x) round(x, 3)))
```


```{r}
# for Control arm
wts.tab.ctl <- res$wts.tab.ctl
wts.tab.ctl.trans <- wts.tab.ctl %>%
  mutate(is_CurePWE = grepl("CurePWE \\(J = \\d+\\)", model)) %>%
  group_by(prior, CurePWE_group = if_else(is_CurePWE, "CurePWE", "PWE")) %>%
  summarize(
    BMA = sum(BMA, na.rm = TRUE),
    `Pseudo-BMA` = sum(`Pseudo-BMA`, na.rm = TRUE),
    `Pseudo-BMA+` = sum(`Pseudo-BMA+`, na.rm = TRUE),
    Stacking = sum(Stacking, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  rename(model = CurePWE_group)
wts.tab.ctl.trans <- wts.tab.ctl.trans[, c("model", "prior", colnames(wts.tab.ctl.trans)[-(1:2)])]

wts.tab.ctl.trans <- wts.tab.ctl.trans %>%
  mutate(
    prior = factor(prior, levels = c("ref", "bhm", "cp", "leap", "npp", "pp", "psipp")), 
    model = factor(model, levels = c("CurePWE", "PWE"))
  ) %>%
  arrange(model, prior)

wts.tab.ctl.trans %>% mutate(across(where(is.numeric), \(x) round(x, 3)))
```


```{r}
wts.tab.trt.trans$arm <- "IFN"
wts.tab.ctl.trans$arm <- "Control"
wts.tab.trans         <- rbind(wts.tab.trt.trans, wts.tab.ctl.trans)

# transform the combined weight table to a long format
wts.tab.trans.long <- wts.tab.trans %>%
  pivot_longer(cols = c(BMA, `Pseudo-BMA`, `Pseudo-BMA+`, Stacking), 
               names_to = "method", values_to = "weight")

# recode prior
wts.tab.trans.long$prior <- recode(
  wts.tab.trans.long$prior, leap = "LEAP", npp = "NPP", pp = "PP~(a[0] == 0.5)", 
  ref = "Reference", bhm = "BHM", cp = "CP", psipp = "PSIPP"
)
wts.tab.trans.long <- wts.tab.trans.long %>% 
  mutate(prior = factor(prior, 
                        levels = c("Reference", "BHM", "CP", "LEAP", "NPP", 
                                   "PP~(a[0] == 0.5)", "PSIPP")), 
         model = factor(model, levels = c("CurePWE", "PWE")))

# create weight plots
wts_plt <- ggplot(wts.tab.trans.long, aes(x = prior, y = weight, fill = model)) +
  geom_bar(stat = "identity", 
           #position = "stack", 
           position = position_dodge(width = 0.8)) +
  facet_grid(method ~ arm) +
  scale_fill_brewer(palette = "Set2", name = "Model") +
  scale_x_discrete(
    labels = function(x) {
      # Parse LaTeX-like labels for display
      sapply(x, function(label) if (label == "PP~(a[0] == 0.5)") parse(text = label) else label)
    }
  )+
  labs(
    title = "Construct Weight Allocation by Treatment Arm across Weighting Methods",
    x = "prior",
    y = "weight"
  ) +
  theme_bw(base_size = 14) +
  theme(legend.position = "bottom",
        legend.text=element_text(size=10),
        legend.key.width= unit(2, 'cm'), 
        legend.margin=margin(),
        strip.text.x = element_text(size = 10),
        strip.text.y = element_text(size = 10),
        #axis.text.x = element_text(angle = 45, hjust = 1),
        plot.title = element_text(hjust = 0.5, size = 14))

wts_plt
## analysis_weights_all, width: 1100, height: 750
```


## Create Tables for Posterior Summaries of 2-Year RFS Probabilities for Each Arm and Treatment Effect

```{r}
# select weighting method
mtd <- "BMA"
# mtd <- "Pseudo-BMA"
# mtd <- "Pseudo-BMA+"
# mtd <- "Stacking"
```


### Posterior Summaries of 2-Year RFS Probabilities for Each Arm

For each treatment arm and prior, display the posterior summary corresponding to the PWE (or CurePWE) model with the highest construct weight (by BMA, Pseudo-BMA, Pseudo-BMA+, or Stacking) among all PWE (or CurePWE) models with varying number of intervals.

```{r}
# function to obtain posterior summaries for each treatment arm
estim.by.arm <- function(samples_list = res$surv.trt.list.all, wts_tab = res$wts.tab.trt){
  samples_list_sub <- samples_list[1:112]
  
  estim <- lapply(samples_list_sub, function(l){
    round(c(mean = mean(l), sd = sd(l)), 3)
  })
  estim <- do.call(rbind, estim) %>%
    as.data.frame()
  estim <- cbind(model = res$models,
                 prior = res$priors,
                 estim) %>%
    as.data.frame()
  rownames(estim) <- NULL
  
  # for the PWE model, under a given prior, keep the row with the highest `mtd` weight across all PWE models
  # apply the same strategy to CurePWE models
  wts_tab_mtd <- wts_tab %>% 
    dplyr::select(model, prior, all_of(mtd)) %>%
    mutate(is_CurePWE = grepl("CurePWE \\(J = \\d+\\)", model)) %>%
    group_by(prior, CurePWE_group = if_else(is_CurePWE, "CurePWE", "PWE")) %>%
    filter(.data[[mtd]] == max(.data[[mtd]])) %>%
    ungroup()
  
  # keep the rows in estim based on matching model and prior in `wts_tab_mtd`
  estim <- merge(
    estim, wts_tab_mtd[, c("model", "prior")], 
    by = c("model", "prior")
  )
  
  estim.ensemble <- lapply(samples_list[113:116], function(l){
    round(c(mean = mean(l), sd = sd(l)), 3)
  })
  estim.ensemble <- do.call(rbind, estim.ensemble) %>%
    as.data.frame()
  estim.ensemble <- cbind(model = rep("Ensemble", 4),
                          prior = c("BMA", "Pseudo-BMA", "Pseudo-BMA+", "Stacking"),
                          estim.ensemble) %>%
    as.data.frame()
  rownames(estim.ensemble) <- NULL
  
  estim <- rbind(estim, estim.ensemble) %>% 
    as.data.frame()
  
  return(estim)
}
```

```{r}
# for IFN arm
estim.trt <- estim.by.arm(samples_list = res$surv.trt.list.all, wts_tab = res$wts.tab.trt)
# for Control arm
estim.ctl <- estim.by.arm(samples_list = res$surv.ctl.list.all, wts_tab = res$wts.tab.ctl)
```


### Posterior Summaries of Treatment Effect (Difference in 2-Year RFS Probabilities)

```{r}
estim.all <- res$estim.all
# find row indices
matching_indices <- integer(nrow(estim.trt) - 4)
for (i in seq_len(length(matching_indices))) {
  matching_indices[i] <- which(
    estim.all$model == estim.trt$model[i] &
    estim.all$prior == estim.trt$prior[i]
  )
}
model_prior_trt <- paste0(sub(" \\(J = \\d+\\)", "", estim.trt$model[1:14]), '_',
                          estim.trt$prior[1:14])
surv.trt.list <- res$surv.trt.list.all[matching_indices]
names(surv.trt.list) <- model_prior_trt

matching_indices <- integer(nrow(estim.ctl) - 4)
for (i in seq_len(length(matching_indices))) {
  matching_indices[i] <- which(
    estim.all$model == estim.ctl$model[i] &
    estim.all$prior == estim.ctl$prior[i]
  )
}
model_prior_ctl <- paste0(sub(" \\(J = \\d+\\)", "", estim.ctl$model[1:14]), '_',
                          estim.ctl$prior[1:14])
surv.ctl.list <- res$surv.ctl.list.all[matching_indices]
names(surv.ctl.list) <- model_prior_ctl

# compute difference in 2 year RFS probabilities
surv.diff.list <- lapply(model_prior_trt, function(i){
  surv.trt.list[[i]] - surv.ctl.list[[i]]
})
surv.diff.list[15:18] <- res$surv.diff.list.all[113:116]

estim.diff <- lapply(surv.diff.list, function(l){
  round(c(mean = mean(l), sd = sd(l),
          quantile2(l, probs = c(0.025, 0.975)),
          prob_greater_0 = mean(l > 0)), 3)
})
estim.diff <- do.call(rbind, estim.diff) %>%
  as.data.frame()

# obtain model and prior
model_prior <- do.call(rbind, strsplit(model_prior_trt, "_")) %>% 
  as.data.frame()

estim.diff <- cbind(model = c(model_prior[, 1], rep("Ensemble", 4)), 
                    prior = c(model_prior[, 2], c("BMA", "Pseudo-BMA", "Pseudo-BMA+", "Stacking")), 
                    estim.diff) %>%
  as.data.frame()
rownames(estim.diff) <- NULL

estim.trt$model <- ifelse(
  grepl("^CurePWE \\(J = \\d+\\)$", estim.trt$model),
  "CurePWE",
  "PWE"
)
estim.trt$model[15:18] <- "Ensemble"

estim.ctl$model <- ifelse(
  grepl("^CurePWE \\(J = \\d+\\)$", estim.ctl$model),
  "CurePWE",
  "PWE"
)
estim.ctl$model[15:18] <- "Ensemble"
```


### Create Tables

```{r}
# construct credible interval as string
textci <- function(lower, upper, digits = 3, mathmode = TRUE) {
  lower.ch <- formatC(lower, digits = digits, format = 'f')
  lower.ch[lower > 0] <- paste0('~', lower.ch[lower > 0])
  upper.ch <- formatC(upper, digits = digits, format = 'f')
  upper.ch[upper > 0] <- paste0('~', upper.ch[upper > 0])
  ci <- paste0('(', lower.ch, ', ', upper.ch, ')')
  if (mathmode)
    ci <- paste0('$', ci, '$')
  ci
}
```

```{r}
ndigits <- 3

estim.combined <- full_join(estim.trt, estim.ctl, by = c("model", "prior"), suffix = c(".trt", ".ctl"))
estim.combined <- full_join(estim.combined, estim.diff, by = c("model", "prior"))

# recode prior names
estim.combined$prior <- recode(
  estim.combined$prior, leap = "LEAP", npp = "NPP", pp = "PP~$(a_0 = 0.5)$", ref = "Reference",
  bhm = "BHM", cp = "CP", psipp = "PSIPP"
)
estim.combined <- estim.combined %>% 
  mutate(prior = factor(prior, 
                        levels = c("Reference", "BHM", "CP", "LEAP", "NPP", "PP~$(a_0 = 0.5)$", "PSIPP",
                                   "BMA", "Pseudo-BMA", "Pseudo-BMA+", "Stacking")), 
         model = factor(model, levels = c("CurePWE", "PWE", "Ensemble"))) %>%
  arrange(model, prior)
tab.estim.combined <- estim.combined %>%
  mutate(CI = textci(`q2.5`, `q97.5`, digits = ndigits)) %>% 
  dplyr::select(-c(`q2.5`, `q97.5`))

tab <- tab.estim.combined %>%
  rename(
    Model = model,
    Prior = prior,
    Mean  = mean,
    SD    = sd,
    `$p(\\Delta > 0 \\mid D)$` = prob_greater_0,
    `$95\\%$ CI`       = CI
  ) %>%
  dplyr::select(Model, Prior, mean.trt, sd.trt, mean.ctl, sd.ctl, Mean, SD, `$p(\\Delta > 0 \\mid D)$`, `$95\\%$ CI`)
colnames(tab)[3:6] <- rep(c("Mean", "SD"), 2)

tab.final <- kbl(tab, format = "latex", booktabs = TRUE,
                 caption = "Posterior Summaries of $\\Delta$ from Individual Constructs and Ensemble Methods",
                 escape = FALSE, digits = ndigits, 
                 align = "llcccccccc") %>%
  add_header_above(c(" " = 2, "IFN" = 2, "Control" = 2, "$\\Delta$" = 4))
```
